Video Understanding : A review of action detection-recognition dataset

### 2024-02-12 conference_101719.tex

The name of each video also carries a meaning, with a specific structure as
follows: \\
\text{vid-name\_class-name\_vible-body-part\_cam-motion\_num-of-people\_cam-viewpoint\_vid-quality}\\
The abbreviations used are listed in Table \ref{config2}. \\
For example, the name
IPL\_Awards\_Ceremony\_shake\_hands\_f\_cm\_np2\_ba\_med\_0.avi represents a
video titled IPL Awards Ceremony, belonging to the shake hands class, with 'f'
indicating full body, 'cm' indicating motion, 'np2' indicating two people, 'ba'
representing back viewpoint, and 'med' indicating medium quality.

\subsection{AVA}

@@

	\item \textbf{Annotation} : Each AMT worker is presented with a video-verb pair and asked to press a Yes or No key signifying if the action is happening in the scene. Positive responses from the first round are sent to subsequent rounds of annotation. Each HIT (a single worker assignment) contains 64 different 3-second videos that are related to a single verb and 10 ground truth videos that are used for control. In each HIT, the first 4 questions are used to train the workers on the task and require the correct answer to be selected before continuing. Only the results from HITs that earn a 90\% or above on the control videos are included in the dataset. The authors run each video in the training set through annotation at least 3 times and require a human consensus of at least 75\% to be considered a positive label. For the validation and test set we increase the minimum number of rounds of annotation to 4 with a human consensus of at least 85\%.

>>>>

The name of each video also carries a meaning, with a specific structure as
follows: \\
\text{vid-name\_class-name\_vible-body-part\_cam-motion\_num-of-people\_cam-viewpoint\_vid-quality}\\
The abbreviations used are listed in Table \ref{config2}. \\
For example, the name
IPL\_Awards\_Ceremony\_shake\_hands\_f\_cm\_np2\_ba\_med\_0.avi represents a
video titled IPL Awards Ceremony, belonging to the shake hands class, with 'f'
indicating full body, 'cm' indicating motion, 'np2' indicating two people, 'ba'
representing back viewpoint, and 'med' indicating medium quality.
\subsection{Sport-1M}

\begin{itemize}
	\item Year : 2014
	\item Paper : Large-scale Video Classification with Convolutional Neural Networks
	Actions \cite{Sports1M}
\end{itemize}
\subsubsection{\textbf{Context and construction perspective}}
In recent years, the rapid growth of Artificial Intelligence has led to the evolution of image-related datasets. However, they were designed to satisfy old traditional Machine Learning methods, such as SVM \cite{HMDB51} \cite{UCF101}. This method is now prone to being left behind by the newborn CNNs method, whose effectiveness was proven by AlexNet \cite{AlexNet} in 2012. The problem arises concerning the equivalent metrics for those datasets. Therefore, a gigantic sports action dataset was developed to address this issue which is called Sports-1M.
\subsubsection{Data collection methods}
The videos are automatically collected from YouTube based on related sports tags. Subsequently, their associated links are stored in a text file for later download. Each clip ensures that the link is accessible before being saved.
\subsubsection{Data distribution}
The dataset contains 1,133,158 YouTube videos, covering a diverse range of content. There are 487 unique classes in the dataset, with each class 
ranging from 1000 to 3000 videos. Notably, each video may be assigned multiple labels, indicating that a single video could have more than one annotation, accounting for approximately 5 \% of the dataset. The dataset is divided into training, validation, and testing sets in a 7:1:2 ratio, respectively.
\begin{itemize}
	\item Train and Validation : 914,491 clips
	\item Test: 218,667 clips
\end{itemize}
\subsubsection{Annotation}
The annotation process was performed automatically by a special machine algorithm. It follows the rule of analyzing the text metadata around the dataset and finding correlations to its labels. First, it identifies associated videos with pre-defined tags and then uses weakly supervised learning to structure the categories into hierarchical levels. For example, in the node "Ball Sports," it can include "freestyle football" and "ball hockey."

Despite the automatic process of acquiring and annotating videos, the portion of duplicated frames are tiny (1755 out of more than 1 million clips). This is primarily attributed to the variability of frames within individual videos. Additionally, variations in actions may happened due to external factors such as camera angles or viewing distances.

Each label describes in detail the associated sports. Therefore, numerous unique and rarely seen sports are also found here.
For example, a line containing a link and labels is found in the training set: \\
\url{https://www.youtube.com/watch?v=BWYPOToJu24} 436,431 \\
The number "436" and "431" indicate its labels in order of "akido" and "grappling"
\subsection{Something Something V2}

\begin{itemize}
	\item Year : 2016
	\item Paper : The “something something” video database for learning and evaluating visual common sense
	Actions \cite{somethingsomething}
\end{itemize}

The recent expansion of the Action Recognition dataset has led to a rapid increase in the number of available videos, particularly sourced from platforms like YouTube such as Sport-1M \cite{Sports1M} and Youtube-8M \cite{YouTube8M}. However, the model's work associated with these datasets still involves combining features extracted from frames, and therefore becoming a "set of image" classification task. That's the reason even these datasets empower models to infer numerous actions depicted in videos, they often lack the contextual understanding of how different actions correlate with each other. Consequently, when an action is combined with various objects, it can potentially mislead the model since it diverges from its learned associations.

As an illustration, consider the action of "pointing" which can result in two scenarios: "Pointing a finger" (Harmless) or "Pointing a knife" (Dangerous). The main objective of Something Something dataset is to address this particular problem.

In the related paper \cite{somethingsomething}, Something V1 emphasizes detailed interactions between human actions and objects, aiming to provide fine-grained videos that reflect real-world aspects. One year after, the V2 version was released in \cite{Somethingv2} and significantly increasing the number of videos and improving label quality.
\subsubsection{Data collection methods}
A group of workers from the crowdsourcing service Amazon Mechanical Turk (AMT) were asked to record and label clips. They recorded videos that demonstrated specific actions with the given labels. After the video is uploaded, it is divided into categories depends on its action, label, and object information. Afterward, they submitted the videos to an online platform, which underwent careful automatic quality checks. Each submission was then rechecked by other workers to make sure there is no mistaken.
\subsubsection{Data distribution}
In the newer V2 version, the number of videos has increased to 220,847 clips, which is twice the number in V1, while retaining the same set of labels totaling 174. Additionally, each clip has been upgraded to a quality of 240px, compared to the previous 100px. Each clip has an average length of 2-6 seconds, demonstrating only a single action mentioned in the its label. Overall, there are 318,572 annotations, which involve 30,408 unique objects. The data is split into training, validation, and test sets with a ratio of 8:1:1. Additionally, measures are taken to ensure that videos created by a single actor are exclusively allocated to one of these three splits. 
\begin{itemize}
	\item Train : 168,913 clips
	\item Validation : 24,777 clips
	\item Test: 27,157 clips
\end{itemize}

An interesting aspect of this dataset is its provision of "sentence-like" information alongside the focus on human actions. This augmentation allows for descriptions of how actors interact with objects. For instance, a video featuring the phrasal verb's action "moving away" might be presented as: "Moving a bag of popcorn away from the camera". By integrating object names with actions, the dataset offers detailed action descriptions.

Due to the unique labeling approach using "natural language," conventional one-hot encoding methods are not applicable. Consequently, it is recommended that model should be first pretrain on ImageNet to enhance the capture of distinctive object characteristics.

For videos in the training set marked by a unique ID, there is an annotated JSON file records detailed descriptions which includes Video IDs (containing only the training video's ID), completed labels (providing precise descriptions of the actor's actions), template categories (outlining the action skeleton), and placeholders (identifying objects used in the video).

For example, a line in JSON file follows:
\begin{itemize}
\item \textbf{id:} 217769
\item \textbf{label:} moving a bag of popcorn away from the camera
\item \textbf{template}: Moving [something] away from the camera
\item \textbf{placeholders}: a bag of popcorn
\end{itemize}
In the testing set, each video is assigned its own true label, which corresponds to the template in the JSON file. For example, the video show that a person is moving a calculator away, it will have the true label "Moving [something] away from the camera".
\subsection{AVA}

@@

	\item \textbf{Annotation} : The AMT workers are shown a pair of videos and verbs and are asked to confirm whether the action is completed in the video or not. The confirmed samples are then annotated. Each HIT (a worker's annotation request) consists of 64 three-second videos related to a single verb, with 10 ground truth videos used for control purposes. Each HIT includes four initial questions that workers must answer correctly in order to proceed. Only the results from HITs that achieve a 90\% or higher accuracy on the control videos are included in the dataset. Each video in the training set must be reviewed at least three times and must receive at least 75\% confirmation from the AMT workers to be considered a positive sample. For the test and validation sets, the authors increase the minimum review frequency to four times and the confirmation rate to 85\%.
